Age-related changes in plant growth and traits

### 2015-04-21 results.Rmd
Example fitting linear model. Closes #11

#Shifts in RA with age

@@

for(n in names(labels.spp)) {
  plot_RAbyAge(n)
}
```
# Individual shoots looked decidedly "less leafy" in many older plants
This led me to wonder how leaf lifespan - or some other variable - was shifting with age

@@

# Plots of individual species show that no species has a significant change either - although several show slight declines at the end
```{r, echo=FALSE,results='hide', message=FALSE}
plot_LLvAge <- function(spp) {
  data2 <- filter(SummaryInd, species==spp)
  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
       main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)

@@

# Several species show significant declines in shoot extension with age
```{r, echo=FALSE,results='hide', message=FALSE}
plot_newlengthvAge <- function(spp) {
  plot(new_length ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leader shoot extention", cex.axis=.8, las=1, pch=16, log="x",
       main=labels.spp[spp])
  points(new_length_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((new_length_mean+new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((new_length_mean-new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
}

mod_newlengthvAge <- function(spp) {
  lm(new_length ~ age, data=subset(SummaryInd,age>2.4 & species==spp))
}

for(n in names(labels.spp)) {
  plot_newlengthvAge(n)
  mod_newlengthvAge(n)
  summary(mod_newlengthvAge(n))
}
```

>>>>

# Shifts in RA with age

@@

for(n in names(labels.spp)) {
  plot_RAbyAge(n)
}
```

# Individual shoots looked decidedly "less leafy" in many older plants
This led me to wonder how leaf lifespan - or some other variable - was shifting with age

@@

# Plots of individual species show that no species has a significant change either - although several show slight declines at the end

```{r, echo=FALSE,results='hide', message=FALSE}
plot_LLvAge <- function(spp) {
  data2 <- filter(SummaryInd, species==spp)
  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
       main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)

@@

# Several species show significant declines in shoot extension with age

```{r, echo=FALSE,results='hide', message=FALSE}

plot_newlengthvAge <- function(data, yvar = "new_length", xvar = "age", ...) {
	Y <- data[[yvar]]
	X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
  # points(new_length_mean ~ age, data=data, cex=1.3, pch=8)
  # points((new_length_mean+new_length_se) ~ age, data=data, cex=1.5, pch=25)
  # points((new_length_mean-new_length_se) ~ age, data=data, cex=1.5, pch=24)
}

summarise_fit <- function(x) {
	data.frame(
		select(glance(x), r.squared, p.value),
		n= length(resid(x)),
		a = coef(x)[1],
		b = coef(x)[2]
	)
}

summarise_all_fits <- function(x) {
	tmp <- lapply(x, summarise_fit) %>%
		bind_rows
	data.frame(species=names(x), tmp)
}

yvar <- "new_length"
xvar <- "age"

data <- filter(SummaryInd, age > 2.4)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_newlengthvAge(data[[spp]], yvar, xvar, log="x",
  	ylim=c(0,150),  main=spp, xlab="age", ylab="leader shoot extention")
  abline(lmfits[[spp]])
}

```
